Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-09 cmsb22.tex
Model size

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the PyBoolNet's repository.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap-spaces) within the timeout of 2 minutes. Number in bold indicate a ratio greater than three.}
  \centering
  \label{tab:pyboolnet_repo}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $e$ & $s$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    arellano\_rootstem &&&& 4 & 0.04 & \textbf{0.31}\\
    calzone\_cellfate &&&& 27 & 0.03 & 0.08\\
    dahlhaus\_neuroplastoma &&&& 32 & 0.04 & 0.11\\
    davidich\_yeast &&&& 12 & 0.03 & 0.08\\
    dinwoodie\_life &&&& 7 & 0.03 & 0.08\\
    dinwoodie\_stomatal &&&& 1 & 0.04 & 0.05\\
    faure\_cellcycle &&&& 2 & 0.04 & 0.04\\
    grieco\_mapk &&&& 18 & 0.04 & 0.08\\
    irons\_yeast &&&& 1 & 0.05 & 0.04\\
    jaoude\_thdiff &&&& 1000+ & \textbf{1.73} & 0.40\\
    klamt\_tcr &&&& 8 & 0.06 & 0.04\\
    krumsiek\_myeloid &&&& 6 & 0.03 & 0.03\\
    multivalued &&&& 4 & 0.02 & 0.02\\
    n12c5 &&&& 5 & \textbf{34.37} & 0.06\\
    n3s1c1a &&&& 2 & 0.02 & 0.03\\
    n3s1c1b &&&& 2 & 0.02 & 0.03\\
    n5s3 &&&& 3 & 0.03 & 0.03\\
    n6s1c2 &&&& 3 & 0.03 & 0.04\\
    n7s3 &&&& 3 & 0.02 & 0.02\\
    raf &&&& 2 & 0.03 & 0.02\\
    randomnet\_n15k3 &&&& 3 & 0.04 & 0.05\\
    randomnet\_n7k3 &&&& 10 & 0.03 & \textbf{0.19}\\
    remy\_tumorigenesis &&&& 25 & \textbf{1.79} & 0.13\\
    saadatpour\_guardcell &&&& 1 & 0.02 & 0.03\\
    selvaggio\_emt &&&& 1000+ & \textbf{1.03} & 0.23\\
    tournier\_apoptosis &&&& 3 & 0.05 & 0.06\\
    xiao\_wnt5a &&&& 4 & 0.06 & 0.03\\
    zhang\_tlgl &&&& 156 & 0.26 & 0.17\\
    zhang\_tlgl\_v2 &&&& 258 & 0.19 & 0.17\\
    \bottomrule
  \end{tabular}

>>>>

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the PyBoolNet's repository.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap-spaces) within the timeout of 2 minutes. Number in bold indicate a ratio greater than three.}
  \centering
  \label{tab:pyboolnet_repo}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $e$ & $s$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    arellano\_rootstem & 9 &&& 4 & 0.04 & \textbf{0.31}\\
    calzone\_cellfate & 28 &&& 27 & 0.03 & 0.08\\
    dahlhaus\_neuroplastoma & 23 &&& 32 & 0.04 & 0.11\\
    davidich\_yeast & 10 &&& 12 & 0.03 & 0.08\\
    dinwoodie\_life & 15 &&& 7 & 0.03 & 0.08\\
    dinwoodie\_stomatal & 13 &&& 1 & 0.04 & 0.05\\
    faure\_cellcycle & 10 &&& 2 & 0.04 & 0.04\\
    grieco\_mapk & 53 &&& 18 & 0.04 & 0.08\\
    irons\_yeast & 18 &&& 1 & 0.05 & 0.04\\
    jaoude\_thdiff & 103 &&& 1000+ & \textbf{1.73} & 0.40\\
    klamt\_tcr & 40 &&& 8 & 0.06 & 0.04\\
    krumsiek\_myeloid & 11 &&& 6 & 0.03 & 0.03\\
    multivalued & 13 &&& 4 & 0.02 & 0.02\\
    n12c5 & 11 &&& 5 & \textbf{34.37} & 0.06\\
    n3s1c1a & 2 &&& 2 & 0.02 & 0.03\\
    n3s1c1b & 2 &&& 2 & 0.02 & 0.03\\
    n5s3 & 4 &&& 3 & 0.03 & 0.03\\
    n6s1c2 & 5 &&& 3 & 0.03 & 0.04\\
    n7s3 & 6 &&& 3 & 0.02 & 0.02\\
    raf & 3 &&& 2 & 0.03 & 0.02\\
    randomnet\_n15k3 & 15 &&& 3 & 0.04 & 0.05\\
    randomnet\_n7k3 & 7 &&& 10 & 0.03 & \textbf{0.19}\\
    remy\_tumorigenesis & 34 &&& 25 & \textbf{1.79} & 0.13\\
    saadatpour\_guardcell & 13 &&& 1 & 0.02 & 0.03\\
    selvaggio\_emt & 56 &&& 1000+ & \textbf{1.03} & 0.23\\
    tournier\_apoptosis & 12 &&& 3 & 0.05 & 0.06\\
    xiao\_wnt5a & 7 &&& 4 & 0.06 & 0.03\\
    zhang\_tlgl & 60 &&& 156 & 0.26 & 0.17\\
    zhang\_tlgl\_v2 & 60 &&& 258 & 0.19 & 0.17\\
    \bottomrule
  \end{tabular}
